What We Eval in the Shadows

### 2021-04-15 paper/main.tex
Example from kaggle

\mypara{Variable lookup and values.}
This corresponds to minimized expressions \c{X}, \c{V}. We also include here lookup to slots in a list or data frame, \ie minimized expression \c{\$}. Variable lookup leads to a large diversity of environments, many being package environments or package environments wrapped in \c{new}.

@@

\todo{Show an actual example with \$}

@@

 \todo{Add an example of a plot with parse from Kaggle}

>>>>

\mypara{Variable lookup and values.}  We also include here lookup to slots in a list or data frame.
This corresponds to minimized expressions \c{X}, \c{V}, and  \c{\$}. Variable lookup leads to a large diversity of environments, many being package environments or package environments wrapped in \c{new}.

@@

@@

In Kaggle, plots are often built with \eval, \c{paste} and \c{ggplot}. In this kernel for the \emph{digit-recognizer} challenge, \c{paste0} is used to generate \c{ggplot} commands featuring unique y labels to build 9 different graphs.

\begin{lstlisting}
p <- lapply(paste0('PC', 1:9), function(pc){
	eval(parse(text=paste0('ggplot(ld, aes(x=label, y=',pc,')) + geom_boxplot()')))
})
\end{lstlisting}
